A scoping review of rodent trapping studies to understand the prevalence of zoonotic disease in West Africa.

### 2021-10-05 reports/manuscript_v2.Rmd
update for appraisal

```{r, figure_5, echo=FALSE, out.width="100%", fig.cap="Presence/absence plots at each unique trapping site for the four most commonly assayed microorganisms Arenaviridae (top), *Bartonella sp.* (second row), *Borrelia sp.* (third row) and *Toxoplasma gondii* (fourth row). The tables to the right of each map highlight the 10 (or number applicable) most commonly positive and tested rodent species and genera assayed."}

knitr::include_graphics(here("figures", "Figure_5a.png"),
                        here("figures", "Figure_5b.png"),
                        here("figures", "Figure_5_legend.png"))

```

>>>>

![Presence/absence plots at each unique trapping site for the four most commonly assayed microorganisms Arenaviridae (top), *Bartonella sp.* (second row), *Borrelia sp.* (third row) and *Toxoplasma gondii* (fourth row). The tables to the right of each map highlight the 10 (or number applicable) most commonly positive and tested rodent species and genera assayed.](../figures/Figure_5_combined.png)
